---
title: "analysis"
author: "Daniel Ward"
date: "29/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Imports
```{r}
library(tidyverse)
library(patchwork)
theme_set(theme_bw())
```


## Read in results
```{r}
df = read_csv("results/general_performance.csv")
df$algorithm[df$algorithm == "rula"] = "RULA"
df$algorithm[df$algorithm == "rwm"] = "RWM"
df$algorithm[df$algorithm == "snle"] = "SNLE"
df
```


## Run times
We can compare the run times of the two algorithms:
```{r}
ggplot(df, aes(y = run_time, x = task, col = algorithm)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "run time / s")
ggsave("plots/run_times.png")
```
Simulations are s significant proportion of the run time. Next we consider a MVN example in julia to look at the cost (per MCMC iteration).

### Run time with number of summary statistics
```{r}
df_s_times = read_csv("results/mvn_times_sum_stats.csv")

df_s_times = df_s_times %>%
  pivot_longer(cols = c(rula_time_per_step, rwm_time_per_step),
               names_to = "Algorithm", values_to = "Time / seconds/step") %>%
  rename("Number of summary statistics" = n_sum_stats)

df_s_times$Algorithm[df_s_times$Algorithm == "rula_time_per_step"] = "RULA"
df_s_times$Algorithm[df_s_times$Algorithm == "rwm_time_per_step"] = "RWM"

p1 = df_s_times %>%
  ggplot(aes(x = `Number of summary statistics`,
             y = `Time / seconds/step`, col = Algorithm)) +
  geom_point() +
  geom_line() +
  theme(legend.position = "none") +
  annotate("text", x=13, y=0.82, label = "θ∈R^10")
p1

```

### Run time with number of parameters
```{r}
df_theta_times = read_csv("results/mvn_times_parameters.csv")

df_theta_times
df_theta_times = df_theta_times %>%
  pivot_longer(cols = c(rula_time_per_step, rwm_time_per_step),
               names_to = "Algorithm", values_to = "Time (seconds/step)") %>%
  rename("Number of parameters" = n_parameters)

df_theta_times$Algorithm[df_theta_times$Algorithm == "rula_time_per_step"] = "RULA"
df_theta_times$Algorithm[df_theta_times$Algorithm == "rwm_time_per_step"] = "RWM"

p2 = df_theta_times %>%
  ggplot(aes(x = `Number of parameters`,
             y = `Time (seconds/step)`, col = Algorithm)) +
  geom_line() +
  geom_point() +
  labs(y = "") +
  annotate("text", x=12.7, y=2.6, label = "s∈R^10")
p2

```

```{r}
p1 + p2
ggsave("plots/run_times_mvn_example.png", width = 8, height = 4)
```

## Effective sample sizes
We can compare the effective sample sizes of the two algorithms. The lines show
the max and min.

```{r}
df %>%
  filter(algorithm != "SNLE") %>%
  ggplot(aes(x = task, y = mean_ess, col = algorithm)) +
    geom_point() +
    geom_pointrange(aes(ymin = min_ess, ymax = max_ess), alpha = 0.5) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    ylab("mean ESS")
ggsave("plots/ess.png")
```

And SNLE effective sample sizes
```{r}
df %>%
  filter(algorithm == "SNLE") %>%
  ggplot(aes(x = task, y = mean_ess, col = algorithm)) +
    geom_point() +
    geom_pointrange(aes(ymin = min_ess, ymax = max_ess), alpha = 0.5) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    ylab("mean ESS")

ggsave("plots/ess_snle.png")

```



## Classification accuracy
```{r}
df %>%
  ggplot(aes(x = task, y = c2st_all, col = algorithm), names_to = c("l")) +
  geom_point() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  lims(y = c(0.5,1)) +
  labs(y = "C2ST")
ggsave("plots/c2st.png")
```

## Thinned classification accuracy
```{r}
df %>%
  ggplot(aes(x = task, y = c2st_thinned, col = algorithm), names_to = c("l")) +
  geom_point() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "C2ST")
ggsave("plots/c2st_thinned.png")
```


## KDE classification accuracy
```{r}
df %>%
  ggplot(aes(x = task, y = c2st_kde, col = algorithm), names_to = c("l")) +
  geom_point() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y = "C2ST")
ggsave("plots/c2st_kde.png")
```


## Acceptance probabilities
```{r}
print(min(df$acceptance_rate, na.rm = TRUE))
print(max(df$acceptance_rate, na.rm = TRUE))
```


```{r}
df %>%
  filter(algorithm == "RWM") %>%
  ggplot(aes(x = task, y = acceptance_rate)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  lims(y = c(0, 0.6))

ggsave("plots/acceptance_rates.png")
```


## KDE check

```{r}
kde_df = read_csv("results/kde_check.csv") %>%
  pivot_longer(cols = c(no_kde_c2st, kde_c2st), values_to = "C2ST", names_to = "KDE")

kde_df$KDE = kde_df$KDE == "kde_c2st"


ggplot(kde_df, aes(x = task, y = C2ST, col = KDE)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


```

